---
title: "linear regression holacracy"
output:
  html_document: default
  pdf_document: default
date: '2023-02-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Loading the dataset

```{r}
library(readxl)
holacracy <- read_excel("C:/Users/szoke/OneDrive/Asztali gép/holacracy.xlsx")
```

Loading the packages

```{r}
library(psych)
library(seminr)
library(tidyverse)
library(car)
library(lares)
library(semTools)
library(stats)
library(interactions)
library(ggplot2)

library(stargazer)
library(lmtest)
```


2. standard data screening

```{r}
summary(holacracy)
```

```{r}
describe(holacracy)
```

3. cleaning the dataset

excluding missing variables

```{r}
table(is.na(holacracy))
#exlude missing variables
holacracynoNA<- holacracy%>%na.omit()
#checking
table(is.na(holacracynoNA))

#renaming the dataset
holacracy<-holacracynoNA
table(is.na(holacracy))
#missing variables are excluded
```

reverse coding items

```{r}
table(holacracy$CC1)
table(holacracy$CC2)
table(holacracy$CC4)


#reverse code

reverse_cols=c("CC1", "CC2", "CC4")
holacracy[, reverse_cols]=6- holacracy[, reverse_cols]

#checking if it was sucess

table(holacracy$CC1)
table(holacracy$CC2)
table(holacracy$CC4)
```


4. creating the constructs

```{r}
attach(holacracy)

holacracy$UICT<- (UICT1+UICT2+UICT3+UICT4+UICT5+UICT6+UICT7+UICT8+UICT9+UICT10+UICT11+UICT12+UICT13+UICT14+UICT15+UICT16+UICT17+UICT18+UICT19+UICT20)/20
holacracy$IC<- (IC1+IC2+IC3)/3
holacracy$TI<- (TI1+TI2+TI3+TI4+TI5+TI6)/6
holacracy$CBI<- (CoCBI1+CoCBI2+CoCBI3+CoCBI4+CoCBI5+CoCBI6+CoCBI7+CoCBI8)/8
holacracy$CC<- (CC1+CC2+CC3+CC4+CC5+CC6+CC7+CC8)/8
holacracy$PS<- (PS1+PS2+PS3+PS4+PS5+PS6+PS7+PS8+PS9+PS10+PS11+PS12)/12
holacracy$OO<- (OO1+OO2+OO3+OO4+OO5+OO6+OO7+OO8+OO9+OO10+OO11+OO12)/12
holacracy$H<- (H1+H2+H3+H4+H5+H6)/6


detach(holacracy)
```

```{r}
describe(holacracy)
```



Outliers and distribution

UICT
outliers
```{r}
boxplot(holacracy$UICT)
holacracy<- subset(holacracy, `UICT`< 4.5)
holacracy<- subset(holacracy, `UICT`> 2.3)
boxplot(holacracy$UICT)
```

distribution
```{r}
multi.hist(holacracy$UICT, main = "", dlty = c("solid", "dashed"))
```

IC
outliers
```{r}
boxplot(holacracy$IC)
holacracy<- subset(holacracy, `IC`> 1.5)
boxplot(holacracy$IC)
```
distribution
 
```{r}
multi.hist(holacracy$IC, main = "", dlty = c("solid", "dashed"))
```


TI
outliers
```{r}
boxplot(holacracy$TI)
holacracy<- subset(holacracy, `TI`> 2.5)
boxplot(holacracy$TI)
```

distribution

```{r}
multi.hist(holacracy$TI, main = "", dlty = c("solid", "dashed"))
```

PS
outliers
```{r}
boxplot(holacracy$PS)

```

distribution

```{r}
multi.hist(holacracy$PS, main = "", dlty = c("solid", "dashed"))
```

OO
outliers
```{r}
boxplot(holacracy$OO)
holacracy<- subset(holacracy, `OO`> 2)
boxplot(holacracy$OO)
```

distribution
```{r}
multi.hist(holacracy$OO, main = "", dlty = c("solid", "dashed"))
```


```




H
outliers

```{r}

#2.5 was the precious
boxplot(holacracy$H)
holacracy<- subset(holacracy, `H`> 3.75)
boxplot(holacracy$H)
```

disribution

```{r}
multi.hist(holacracy$H, main = "", dlty = c("solid", "dashed"))
```


Testing the assumptions (Normality, linearity, independence, homoscedasticity, no mullticollinarity, no autocorrelation)

Checking for multicollinarity

```{r}
#testing for multicolleanirity --> correlation matrix
cor_matrix<- cor(holacracy[, c("UICT", "TI", "CC", "PS", "IC", "OO", "CBI")])

corPlot(cor_matrix)
```


Checking linearity and homoscedasticity


```{r}



scatterplot(holacracy$UICT~holacracy$TI)
#linearity of the data

lm1<- lm(UICT~IC,
         data=holacracy)


lm2<- lm(UICT~IC*H-H, data = holacracy)


```

Testing the assumptions

```{r}
par(mfrow=c(2,2))
plot(lm1)
#normality seems to be okay
```


```{r}
#testing for homoscedasicity
bptest(lm1)
bptest(lm2)
```

homoscedasticity is not violated

```{r}
#test for autocorrelation

dwtest(lm1)
dwtest(lm2)

#output is close to 2, p value is greater than 0.05 so there is no autocorrelation
```


H3 and H4

```{r}
scatterplot(holacracy$UICT~holacracy$OO)
#line is close to be linear

lm11<- lm(UICT~OO,
         data=holacracy)

lm12<- lm(UICT~OO*H-H, data = holacracy)


par(mfrow=c(2,2))
plot(lm11)
```

```{r}

#testing for homoscedasicity
bptest(lm11)
bptest(lm12)


```


```{r}
dwtest(lm11)
dwtest(lm12)
```




H5 and H6

```{r}

scatterplot(holacracy$UICT~holacracy$PS)
#doesn't seem linear relationship

lm9<- lm(UICT~PS,
         data=holacracy)

lm10<- lm(UICT~PS*H-H, data = holacracy)



```

testing the assumptions

```{r}
par(mfrow=c(2,2))
plot(lm9)
```

```{r}
#testing for homoscedasicity
bptest(lm9)
bptest(lm1)
```

```{r}
dwtest(lm9)
dwtest(lm10)
```



H7 and H8

```{r}
scatterplot(holacracy$UICT~holacracy$TI)


lm3<- lm(UICT~TI,
         data=holacracy)

lm4<- lm(UICT~TI*H-H, data = holacracy)


lm3.1<- lm(log(holacracy$UICT)~log(holacracy$TI),
         data=holacracy)
summary(lm3.1)
par(mfrow=c(2,2))
plot(lm3)

```

```{r}
par(mfrow=c(2,2))
plot(lm3)
```


```{r}
fit <- lm( holacracy$UICT  ~ poly(holacracy$TI, 1))
summary(fit)
```





```{r}
bptest(lm3)
bptest(lm4)
```

Above the cut value but just slightly (lm3)

```{r}
dwtest(lm3)
dwtest(lm4)
```



H9 and H10 

```{r}
scatterplot(holacracy$UICT~holacracy$CC)

lm7<- lm(UICT~CC,
         data=holacracy)

lm8<- lm(UICT~CC*H-H, data = holacracy)



```

```{r}
par(mfrow=c(2,2))
plot(lm8)
```
```{r}
bptest(lm7)
bptest(lm8)
```

```{r}
dwtest(lm7)
dwtest(lm8)
```




H11 and H12
CBI
outliers
```{r}
boxplot(holacracy$CBI)
holacracy<- subset(holacracy, `CBI`> 2.5)
boxplot(holacracy$CBI)
```




```{r}
scatterplot(holacracy$UICT~holacracy$CBI)


lm5<- lm(UICT~CBI,
         data=holacracy)

lm6<- lm(UICT~CBI*H-H, data = holacracy)


par(mfrow=c(2,2))
plot(lm5)

```



```{r}
summary(lm1)
summary(lm3)
summary(lm5)
summary(lm7)
summary(lm9)
summary(lm11)

stargazer(lm1, lm3, lm5, lm7, lm9, lm11,  type = "text",
          out = "lm1newnew.txt")
```



creating the model by adding easch variable one by one

```{r}


l1<- lm(UICT~IC,
         data=holacracy)
summary(l1) 

l2<- lm(UICT~IC + OO,
         data=holacracy)
summary(l2)

l3<-lm(UICT~IC + OO +PS,
         data=holacracy)
summary(l3)

l4<-lm(UICT~IC+OO+PS+TI,
         data=holacracy)
summary(l4)         
l5<-lm(UICT~IC+OO+PS+TI+CC,
         data=holacracy)
summary(l5)

l6<-lm(UICT~IC+OO+PS+TI+CC+CBI,
         data=holacracy)
         
summary(l6)  

l7<- lm(UICT~IC+OO+PS+TI+CC+CBI+IC*H-H+OO*H-H +PS*H-H + TI*H-H + CC*H-H + CBI*H-H,
         data=holacracy)
l8<- lm(UICT~IC+OO+PS+TI+CC+CBI+IC*H-H+OO*H-H +PS*H-H + TI*H-H + CC*H-H + CBI*H-H+ Satisfaction+ Industry+ Size+ Age+ Gender+ Education+ Nationality,
         data=holacracy)         
summary(l7)         
summary(l8)
stargazer(l1, l2, l3, l4, l5, l6, l7, l8,  type = "text",
          out = "lm1.txt",
          columns = c(1:8),
          width = 2)
```

alternative model specification

```{r}

holocpath<-'
IC~H
TI~H
CBI~H
CC~H
PS~H
OO~H
UICT~IC
UICT~TI
UICT~CBI
UICT~CC
UICT~PS
UICT~OO
'

holocpath1<- lavaan::sem(holocpath, data = holacracy, se = "standard", mimic = "eqs")
summary(holocpath1, standardized=TRUE, fit.measures=TRUE, rsq=TRUE)
library(lavaanPlot)
lavaanPlot(model=holocpath1, coefs = TRUE, covs=FALSE, stand = TRUE,  stars = c("regress"))


```




confirmatory factor analysis

```{r}
library(readxl)
holacracy <- read_excel("C:/Users/szoke/OneDrive/Asztali gép/holacracy.xlsx")
```


```{r}
library(psych)
library(tidyverse)
library(car)
library(lares)
library(semTools)
library(stats)
library(interactions)
library(ggplot2)


library(stargazer)
library(lmtest)
library(car)
library(tidyverse) 
library(psych)
library(corpcor)
library(car)
library(lares)
library(lavaan)
library(lavaanPlot)
library(GPArotation)
library(parameters)
library(nFactors)
library(readxl)
```


```{r}
table(is.na(holacracy))
#exlude missing variables
holacracynoNA<- holacracy%>%na.omit()
#checking
table(is.na(holacracynoNA))

#renaming the dataset
holacracy<-holacracynoNA
table(is.na(holacracy))
#missing variables are excluded
```

```{r}
CFA.01<- '
UICT=~ UICT1+UICT2+UICT3+UICT4+UICT5+UICT6+UICT7+UICT8+UICT9+UICT10+UICT11+UICT12+UICT13+UICT14+UICT15+UICT16+UICT17+UICT18+UICT19+UICT20
IC=~ IC1+IC2
TI=~ TI1+TI2+TI3+TI4+TI5+TI6
CBI=~ CoCBI1+CoCBI2+CoCBI3+CoCBI4+CoCBI5+CoCBI6+CoCBI7+CoCBI8
CC=~ CC1+CC2+CC3+CC4+CC5+CC6+CC7+CC8
PS=~ PS1+PS2+PS3+PS4+PS5+PS6+PS7+PS8+PS9+PS10+PS11+PS12
OO=~ OO1+OO2+OO3+OO4+OO5+OO6+OO7+OO8+OO9+OO10+OO11+OO12
H=~H1+H2+H3+H4+H5+H6
'
FIT.CFA.01<- cfa(CFA.01, data=holacracy, se="standard", mimic="EQS")
summary(FIT.CFA.01, standardized=TRUE, fit.measures=TRUE)

lavaanPlot(model=FIT.CFA.01, coefs = TRUE, covs=TRUE, stand = TRUE,  stars = c("regress", "latent"))
```



